\pkg{Rgbp}: Bayesian Hierarchical Modeling and Frequentist Method Check

### 2013-04-13 jss/article.tex
intv.low - > low.intv

Once we are sure that the assumption of an additional hierarchy is reasonable, we start a model-fitting process.  Since the true death rate after CABG surgery might be small and caseloads ($n_{j}$) look relatively much bigger than the number of deaths ($z_{j}$), the Poisson distribution would be our first choice to describe the uncertainty in our data. Next, \code{gbp} will help us fit a multi-level model with the Gamma conjugate distribution for $\lambda_{j}$ on the second-level hierarchy whose mean is 0.02 ($\lambda_{0}=0.02$) as described in the section 3.2.
\begin{CodeChunk}
\begin{CodeInput}
R> p <- gbp(z, n, mean.PriorDist = 0.02, model = "pr")
R> p
\end{CodeInput}
\begin{CodeOutput}
Summary for whole observations:

>>>>

Assuming an additional hierarchy is reasonable, a model-fitting process begins.  Since the true death rate per exposure after CABG surgery might be small and the caseloads ($n_{j}$) look relatively much bigger than the number of deaths ($z_{j}$), the Poisson distribution would be our first choice to describe the uncertainty in our data. Next, \code{gbp} will help us fit the Poisson multi-level model with the Gamma conjugate prior distribution on the true death rate $\lambda_{j}$ whose mean is 0.02 ($\lambda_{0}=0.02$) as described in 3.2 . For reference, the number of regression coefficients ($m$) is 0 because we do not need to estimate the prior mean via any regression.
\begin{CodeChunk}
\begin{CodeInput}
R> p <- gbp(z, n, mean.PriorDist = 0.02, model = "pr")
R> p
\end{CodeInput}
\begin{CodeOutput}
Summary for whole observations:
